Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
More saturation 1 lemmata

\todo{Move this lemma:}
\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.  
Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\tau $.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\section{Further Research}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
\end{itemize}

>>>>

\todo{Move this lemma:}
\begin{lem}\label{lem:add_point_effective_divisor_no_deg_1_generators}
Let $(X,\Delta,\halfcan)\to (X,\Delta',\halfcan)$ be the natural map of genus $g$ log curves with $\Delta=\Delta'+P$, such that $2\halfcan\sim K_X+\Delta$, $2\halfcan'\sim K_X+\Delta'$, and $\Delta=\Delta'+P$ with $\Delta'\ne 0$ for some $P\not\in supp(\halfcan)$.  
Suppose $\deg(\lfloor{\halfcan}\rfloor)=\deg(\lfloor \halfcan'\rfloor)\ge 0$, so $R_{\halfcan}$ has a
generator $u$ in degree 1, and $R_{\halfcan'}$ has no new generators in degree 0.  Suppose $D$ is generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1, y_2, y_3$ in degrees 2, 2, and 3 respectively.  
\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j \rangle \\
										 &+ \langle y_3^2, y_3y_2, y_2y_1, y_1^2\rangle \\
\end{align*}
\item A Grobner basis with initial terms described above minimally generates $I'$ over $I$.
\end{itemize}
\end{lem}
\begin{proof}
Similar to all the other lemmas\todo{combine sections?}
\end{proof}

\begin{lem}\label{lem:add_point_effective_divisor_deg_1_but_not_deg_2_generators}
Let $2\halfcan=K_X$ of a non-stacky curve $X$ such that $h^0(X, \halfcan) > 0$.  Then for any point $P$, 
\[
	H^0(X, \halfcan+P)=H^0(X,\halfcan).
\]
\end{lem}
\begin{proof}
\todo{add proof}
\end{proof}

@@

\section{Further Research}
\begin{itemize}
	\item More on fractional modular forms
	\item Make explicit generators and relations for base case of non-stacky higher genus half-canonical divisors
	\item In the case $g \geq 2$, can the bound from Proposition ~\ref{prop:relation_generation} be reduced from 11 to 10 (which would then be sharp by Remark ~\ref{rem:relations_generation_ten})? \todo{Possibly think more about this} 
	\item Generic Initial ideal (and other genericness properties?)
\end{itemize}
